---
title: "MATH 012: Week 14"
date: "Minitab Lab 10"
output: rmdformats::html_docco
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This week, let's delve into **hypothesis testing for the population mean**. For our discussion, let's suppose our interest lies in the population mean height, denoted as $\mu$, for **all Lehigh students**. As this value is unknown, we need to collect a sample for inference. For our purpose, let's utilize the class survey data with the **Height** variable.

```{r,echo=FALSE}
library(knitr)
library(kableExtra)
survey<-read.csv('https://www.lehigh.edu/~tak422/data/Survey_2023.csv')
survey %>%
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "350px")
```

Download the survey data (a .csv file) from this [**LINK**](https://drive.google.com/file/d/1kPnc2Uw7pPl6AzxS0TgDb_ML31NxyEoG/view?usp=sharing),\
then open the [**Minitab**](https://app.minitab.com/) user interface and proceed to answer the following questions.

In this question, the random sample assumption is violated. However, we acknowledge this limitation and proceed with the hypothesis testing to confirm:
\[
H_0:\; \mu = 66.1\;\;\text{vs.}\;\;H_a:\; \mu > 66.1
\]
under 0.1 significance level.

1. Output the descriptive statistics of **Height** variable and record the estimated standard error (SE Mean). 

2. Perform the hypothesis testing through **Minitab** (Star => Basic Statistics => **1-sample Z for the Mean**). Given significance level, would you reject the null hypothesis in favor of the alternative hypothesis?  

For hypothesis testing procedures, if the corresponding sample size is small ($n<30$) and the population standard deviation $\sigma$ is unknown, then we need to use t-distribution (instead of standard normal distribution) for the p-value calculation. Let us now consider a similar hypothesis test for another target parameter $\mu$, the population mean height for **all MALE Lehigh students**:
\[
H_0:\; \mu = 69\;\;\text{vs.}\;\;H_a:\; \mu > 69
\]
under 0.1 significance level.

3. Subset the survey dataset to include only the rows where the **Gender** variable is Male. Note that we only have 21 observations.

4. Perform the hypothesis testing through **Minitab** (Star => Basic Statistics => **1-sample t for the Mean**). Given significance level, would you reject the null hypothesis in favor of the alternative hypothesis?  

   

