---
title: "MATH 012: Week 5"
date: "Minitab Lab 4"
output: rmdformats::html_docco
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The following is a real estate data with 414 observations and 7 variables
```{r,echo=FALSE}
library(knitr)
library(kableExtra)
survey<-read.csv('https://www.lehigh.edu/~tak422/data/Real_estate.csv')
survey %>%
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "250px")
```
|Variable | Description |
|:------------|:--------------|
|**X1** | Transaction date|
|**X2**| House age |
|**X3**| Distance to the nearest MRT station|
|**X4**| Number of convenience stores|
|**X5**| Latitude|
|**X6**| Longitude|
|**Y**| House price of unit area|

Download data (.csv file) from this [**LINK**](https://drive.google.com/file/d/12aNlOShZH8wHcKDAnbbI8fpWvUeENAhg/view?usp=sharing), then open the [**Minitab**](https://app.minitab.com/) user interface and proceed to answer the following questions.

1. Check out the correlations and scatter plots between the response variable **Y** and potential predictor variables **X**s. Do you think there is a predictor variable that can be used for a linear regression analysis?

2. If you cannot find one, then let us transform data. Go to Calc => Calculation and use a log function, **LN()**, to transform **X3**. Save it in **LOG_X3** and check the correlation and scatter plot between **LOG_X3** and **Y**. Do you think we can use the transformed variable for the regression analysis?

3. Perform a linear regression analysis by Minitab. 
-   What are the values of slope and intercept? Do you think you can interpret those? 
-   What is the coefficient of determination? Can you interpret the value?

4. Predict the value of **Y** when **LOG_X3** is 5.25.



