---
title: "MATH 012: Week 3"
date: "Minitab Lab 2"
output: rmdformats::html_docco
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's revisit our class survey data, which comprises 15 variables and 79 observations:
```{r,echo=FALSE}
library(knitr)
library(kableExtra)
survey<-read.csv('https://www.lehigh.edu/~tak422/data/Survey_2023.csv')
survey %>%
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "250px")
```

Download the survey data (.csv file) from this [**LINK**](https://drive.google.com/file/d/1kPnc2Uw7pPl6AzxS0TgDb_ML31NxyEoG/view?usp=sharing),\
then open the [**Minitab**](https://app.minitab.com/) user interface and proceed to answer the following questions.

1. For the variable **Shoes**, compute the mean, median, variance, standard deviation, range, and IQR. 

2. Create a boxplot for the variable **Shoes** in horizontal orientation. 
Determine whether it exhibits a right-skewed, left-skewed, or symmetric distribution.

3. Create side-by-side horizontal boxplots for the variable **Shoes** categorized by different groups of the **Gender** variable. 
Assess which group demonstrates a higher central tendency and which one exhibits lower variability among females and males.

4. Duplicate the **Shoes** variable to a new variable, **Shoes_1**. Remove the two outliers from **Shoes_1**.

5. For the variable **Shoes** and **Shoes_1**, calculate the mean, median, variance, standard deviation, range, and IQR. 
Determine which numerical measures are sensitive or resistant to outliers.





