---
title: "MATH 012: Week 12"
date: "Minitab Lab 9"
output: rmdformats::html_docco
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We covered the concept of confidence intervals in class. A prevalent challenge in statistical inference is the computational burden, particularly with large sample sizes. Fortunately, a computing package like **Minitab** can alleviate this issue, proving valuable for your future studies. 

Suppose we are interested in the population mean height, denoted as $\mu$, for all Lehigh students. Since this value is unknown, we need to collect a sample to make an inference. Fortunately, we have data ("Height" variable) from our class survey.

```{r,echo=FALSE}
library(knitr)
library(kableExtra)
survey<-read.csv('https://www.lehigh.edu/~tak422/data/Survey_2023.csv')
survey %>%
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "350px")
```

Download the survey data (a .csv file) from this [**LINK**](https://drive.google.com/file/d/1kPnc2Uw7pPl6AzxS0TgDb_ML31NxyEoG/view?usp=sharing),\
then open the [**Minitab**](https://app.minitab.com/) user interface and proceed to answer the following questions.


1. Let's begin by checking the assumptions. (It's worth noting that one of the assumptions is violated. However, for the sake of our discussion, let's consider it a limitation and proceed.)
   
   
2. Output the descriptive statistics of **Height** variable and calculate the three components: point estimate, cut-off $Z_{\alpha/2}$, and (estimated) standard error.

3. Derive the confidence interval for the population mean height $\mu$ by hands. Note that we can replace the population standard deviation with the sample standard deviation for large sample sizes, $n$.

4. Now, compute the confidence interval through **Minitab** (Star => Basic Statistics => **1-sample Z for the Mean**).  Compare the result with the previous one from the hand calculation.


   

