---
title: "MATH 012: Week 4"
date: "Minitab Lab 3"
output: rmdformats::html_docco
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's revisit our class survey data, which comprises 15 variables and 79 observations:
```{r,echo=FALSE}
library(knitr)
library(kableExtra)
survey<-read.csv('https://www.lehigh.edu/~tak422/data/Survey_2023.csv')
survey %>%
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "250px")
```

Download the survey data (.csv file) from this [**LINK**](https://drive.google.com/file/d/1kPnc2Uw7pPl6AzxS0TgDb_ML31NxyEoG/view?usp=sharing),\
then open the [**Minitab**](https://app.minitab.com/) user interface and proceed to answer the following questions.

1. Create a contingency table for **Gender** (in rows) and **Sports** (in columns) variables to show the relative frequency, i.e., unconditional percentage. What is the reason we cannot simply compare males and females with respect to different sports using this contingency table?

2. Generate a conditional contingency table to compare males and females with respect to different sports. Excluding "Other" category, which sport is more popular among male students compared to female students?

3. Among the continuous variables, which pair do you believe has the highest correlation? Compute the correlations to confirm your guess.

4. Create scatter plots with **MO_Height** on the X-axis and **Height** on the Y-axis, segmented by the **Gender** variable. Which gender exhibits a stronger positive relationship?



