---
title: "Minitab Lab 1"
date: "2023-08-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r,echo=FALSE}

```
## Minitab Lab for Recitation 1

<font size = "3">Our class survey data contains the survey information about 11 variables and 83 observations. The following is a part of data:</font>
```{r,echo=FALSE}
library(knitr)
survey<-read.csv('https://www.lehigh.edu/~tak422/data/Survey_MATH12.csv')
kable(survey[1:11,])
```
<font size = "3">
Let us download the survey data (an excel file) through this [LINK](https://drive.google.com/file/d/1DlQuNSYGLpGSXMMH6D0lnIqdV4oDULsc/view?usp=sharing). 
Open **Minitab** user interface and load the data.

1. Choose one of the discrete numercal variables and calculate the mean.

2. Choose one of the continuous numerical variables and calculate the median.

3. Choose one of the categorical variables and make a pie chart. 

4. Make a histogram for the variable Shoes. Don't forget to use relative frequency or percentage for each rectangle. 
</font>



