---
title: "MATH 012: Week 2"
date: "Minitab Lab 1"
output: rmdformats::html_docco
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Our class survey data contains 15 variables and 79 observations:
```{r,echo=FALSE}
library(knitr)
library(kableExtra)
survey<-read.csv('https://www.lehigh.edu/~tak422/data/Survey_2023.csv')
survey %>%
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "350px")
```

You can download the survey data (a .csv file) through this [**LINK**](https://drive.google.com/file/d/1kPnc2Uw7pPl6AzxS0TgDb_ML31NxyEoG/view?usp=sharing).\
Open [**Minitab**](https://app.minitab.com/) user interface and load the data.\
Answer the following questions.

1. Choose one of the categorical numerical variables and draw a frequency table.

2. Choose one of the discrete numerical variables and draw a frequency table.

3. Choose one of the categorical variables and make a pie chart. 

4. Make a histogram for the variable Height. Don't forget to use relative frequency or percentage for each rectangle. 




